Stressing Bank Profitability for Interest Rate Risk$^*$

### 2013-07-10 LATEX/beg.draft.2013.tex
I made a change to check things

\vspace{-0.1in}
Regular bank stress testing (and the capital planning that it implies) is one of the three complementary reforms that has been made to U.S. capital regulation in response to the shortcomings of the pre-crisis regime.\renewcommand{\baselinestretch}{1}\footnote{See Governor Tarullo's November 2011 speech ``The Evolution of Capital Regulation'' for this characterization of stress testing. The two other reforms that he mentions are improvements to the traditional, individual firm approach to capital regulation and the introduction of a macroprudential component to capital regulation.\vspace{0.05in}}\renewcommand{\baselinestretch}{1.5} While stress testing can take many forms---for example, being based on a small number of scenarios, being based on a large number of scenarios, or even being undertaken in reverse form to achieve a certain adverse outcome---the form of the stress tests mandated under the Dodd-Frank Act for the Federal Reserve to undertake and the form being used by the Federal Reserve for its annual Comprehensive Capital Analysis and Review (CCAR) is one based around a small number of scenarios.  This approach involves specifying a small number of macroeconomic and financial scenarios that represent stressful conditions over the time horizon of the stress test and then projecting, for each bank holding company (BHC) in the stress test, its losses, income, and path of capital \textit{given that scenario}. Accordingly, there are at least two important parts to conducting bank stress tests (i)~formulating macroeconomic and financial scenarios that should be stressful to banks and (ii)~developing econometric models that are able to translate such stressful conditions into losses, income, and capital.

>>>>

\vspace{-0.1in}
AAA Regular bank stress testing (and the capital planning that it implies) is one of the three complementary reforms that has been made to U.S. capital regulation in response to the shortcomings of the pre-crisis regime.\renewcommand{\baselinestretch}{1}\footnote{See Governor Tarullo's November 2011 speech ``The Evolution of Capital Regulation'' for this characterization of stress testing. The two other reforms that he mentions are improvements to the traditional, individual firm approach to capital regulation and the introduction of a macroprudential component to capital regulation.\vspace{0.05in}}\renewcommand{\baselinestretch}{1.5} While stress testing can take many forms---for example, being based on a small number of scenarios, being based on a large number of scenarios, or even being undertaken in reverse form to achieve a certain adverse outcome---the form of the stress tests mandated under the Dodd-Frank Act for the Federal Reserve to undertake and the form being used by the Federal Reserve for its annual Comprehensive Capital Analysis and Review (CCAR) is one based around a small number of scenarios.  This approach involves specifying a small number of macroeconomic and financial scenarios that represent stressful conditions over the time horizon of the stress test and then projecting, for each bank holding company (BHC) in the stress test, its losses, income, and path of capital \textit{given that scenario}. Accordingly, there are at least two important parts to conducting bank stress tests (i)~formulating macroeconomic and financial scenarios that should be stressful to banks and (ii)~developing econometric models that are able to translate such stressful conditions into losses, income, and capital.
